### 2019-05-06 papers/haskell19/8-conclusions.tex
Pass over Section 8

We presented a novel approach for automatically deriving flexibe random
generators inspired by the seminal work on Data Types \`a la Carte.
%
Furthermore, we incorporate valuable structural information into our generation
process by considering not only data constructors but also the information
statically available in abstract interfaces and functions' pattern matchings.

In the future, something something...

>>>>

We presented a novel approach for automatically deriving flexible random
generators inspired by the seminal work on Data Types \`a la Carte.
%
Furthermore, we incorporate valuable structural information into our generation
process by considering not only data constructors, but also the information
statically available in abstract interfaces and functions' pattern matchings.

In the future, we aim to minimize the runtime overhead of our technique, using
perhaps prefix-free encodings based on generation frequencies, as a way to
reduce the representation bureaucracy as much as possible.
%
Additionally, we are interested on including additional sources of structural
information from the users' codebases, e.g., locally defined patterns or
sequences of functions applications.
%
Interesting thoughts to motivate our future research.
